SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios

### 2015-12-03 papers/B1555_EdgeOn/B1555_letter.tex
Shifted order of a couple of paragraphs in the last section

\textbf{
Here, we find evidence for an edge-on disc in the flux-ratio
  anomaly gravitational lens B1555+375 that can also account for the
  required perturbation in the mass model. Such high-order deviations
  from a smooth mass distribution have already been suggested
  previously \citep{evans03, congdon05}, but this is the first time
  that an observed disc has been explicitly modelled to account for a
  flux-ratio anomaly. However, it is important to realise that by
  including observationally-motivated additional components/modification[?] to a `smooth' mass
  distribution, such as luminous dwarf companions or edge-on discs, in
  the mass models, we are still limited in our interpretation since we
  must assume that the anomalies are due exclusively to these
  additional components. For B1555+375, it may be possible to independently constrain the mass of the disc 		through kinematic measurements (most likely from mm-wavelength resolved emission line observations), which 	would test whether the disc makes a sufficient contribution to the mass model \citep[e.g. as in the case of 	B1933+503;][]{suyu12}. Also, in the blue contours of Fig.~\ref{fig:merlin}, B1555+375 shows evidence for an extended $\sim$ 100 mas gravitational arc at radio wavelengths that crosses the edge-on disc. Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the disc is sufficient to cause the anomaly.}

\textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies. Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account 
\citep[e.g.][]{Xu15}. This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
  be measured using narrow lines \citep[e.g.][]{N14}. Finally, near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components.}
  %Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems \citep[and the presence of a disc-like component may not resolve the anomaly anyway;][]{evans03}, indicating that these systems are still useful for probing the dark matter substructure mass function.

>>>>

\textbf{
Here, we find evidence for an edge-on disc in the flux-ratio
  anomaly gravitational lens B1555+375 that can also account for the
  required perturbation in the mass model.  Moreover, near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components. Such high-order deviations
  from a smooth mass distribution have already been suggested
  previously \citep{evans03, congdon05}, but this is the first time
  that an observed disc has been explicitly modelled to account for a
  flux-ratio anomaly. However, it is important to realise that by
  including observationally-motivated additional components/modification[?] to a `smooth' mass
  distribution, such as luminous dwarf companions or edge-on discs, in
  the mass models, we are still limited in our interpretation since we
  must assume that the anomalies are due exclusively to these
  additional components. For B1555+375, it may be possible to independently constrain the mass of the disc through kinematic measurements (most likely from mm-wavelength resolved emission line observations), which 	would test whether the disc makes a sufficient contribution to the mass model \citep[e.g. as in the case of 	B1933+503;][]{suyu12}. Also, in the blue contours of Fig.~\ref{fig:merlin}, B1555+375 shows evidence for an extended $\sim$ 100 mas gravitational arc at radio wavelengths that crosses the edge-on disc. Further high resolution imaging with very long baseline interferometry will provide the observational constraints required to fully test whether the disc is sufficient to cause the anomaly.}

\textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies. Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, therefore, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account 
\citep[e.g.][]{Xu15}. This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
  be measured using narrow lines \citep[e.g.][]{N14}.}
  %Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems \citep[and the presence of a disc-like component may not resolve the anomaly anyway;][]{evans03}, indicating that these systems are still useful for probing the dark matter substructure mass function.
